Using Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2020-12-09 thesis/thesis.tex
thesis: Add NGC 2682 results

>>>>

\subsection{NGC 2682}

\begin{figure}[H]
  \vfil
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_pm_filtered_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_filtered_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_filtered_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 DEC (filtered) characterization.}
\end{figure}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 0 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2682 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2682}
  \end{center}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -10.9737 $\pm$ 0.0064 & -2.9396 $\pm$ 0.0063 & 1.1325 $\pm$ 0.0011 & 1194 \\
      Clusterix+TOPCAT & -10.970 $\pm$ 0.322 & -2.958 $\pm$ 0.327 & 1.142 $\pm$ 0.080 & 649 \\
      KMeans & -8.616 $\pm$ 5.591 & -3.710 $\pm$ 6.067 & 1.196 $\pm$ 0.226 & 1374 \\
      DEC & -8.926 $\pm$ 5.278 & -3.550 $\pm$ 5.425 & 1.144 $\pm$ 0.159 & 1238 \\
      \textbf{DEC (filtered)} & -9.619 $\pm$ 4.112 & -3.317 $\pm$ 3.976 & 1.140 $\pm$ 0.089 & 990 \\
    \end{tabular}
    \caption{NGC 2682 results.}
    \label{tab:results_ngc_2682}
  \end{center}
\end{table}
